% !TEX root = ../main.tex

\newfootnotes{a}
\anotecontent{token}{TokenHook deployed on Rinkeby at \url{https://bit.ly/33wDENx} (Solidity) and \url{https://bit.ly/3dXaaPc} (Vyper). Mainnet at \url{https://bit.ly/35FMbAf} (Solidity 0.5.11)}

\anotecontent{cas}{A lock-free synchronization strategy that allows comparing and setting values atomically.}

\anotecontent{interactions}{Etherscan: \url{https://bit.ly/33xHfL2}, \url{https://bit.ly/35TimMW} and \url{https://bit.ly/3eFAnAZ}.}

\anotecontent{versions}{Compatible Solidity version of TokenHook (v. 0.5.11) deployed on Mainnet at \url{https://bit.ly/35FMbAf} and the latest Solidity (v. 0.8.4) on Rinkeby \url{https://bit.ly/3tI139S}. Vyper code at \url{https://bit.ly/3dXaaPc}.}

\anotecontent{active}{In actively managed funds, investment managers actively buy and sell assets with the goal of outperforming a specified benchmark index, resulting in higher management fees.}

\anotecontent{btc-perp}{A type of Bitcoin futures contract without a defined expiration date (known as a ``perpetual'').}

\anotecontent{liquidity}{The more liquid an asset is, the easier and more efficient it is to convert back into cash. Less liquid assets take more time and may incur higher costs~\cite{Investo_Liquidity}.}

\anotecontent{long-short}{Going long refers to buying an asset with the expectation that its value will increase, allowing it to be sold for a profit later. Conversely, going short refers to profiting from a decline in the price~\cite{Investo_LongShort}.}

\anotecontent{risk}{In 2018, Credit Suisse had to close an LETF ETN after its price plunged 90\% in one day. In another example, WisdomTree had to close its 3x oil products in March 2020 after their value was wiped out~\cite{FT_LETF}.}

\anotecontent{open-end}{Open-end funds can issue an unlimited number of shares. The fund sponsor sells shares directly to investors and redeems them as well. The NAV per share of an open-end fund is calculated daily by dividing the total value of the fund (minus liabilities) by the total number of shares outstanding~\cite{Investo_OpenEnd}.}

\anotecontent{Pseudo}{A cryptocurrency that is not sufficiently decentralized~\cite{Pseudo}.}

\anotecontent{FTX-ETCBULL}{ETCBULL transactions on the Ethereum blockchain filtered for issued and deposited tokens to FTX's own address: \url{https://bit.ly/3MwHVqv}.}

\anotecontent{FTX-XRPBULL}{List of XRPBULL holders: \url{https://bit.ly/3MQurrc}.}

\anotecontent{FTX-ADABULL}{List of ADABULL holders: \url{https://bit.ly/3MUxPRZ}.}

\anotecontent{fungible}{Fungible (interchangeable) token standards are widely used by decentralized applications (dApps) to interact with other applications. ERC-20 is the dominant standard, followed by ERC-777 and ERC-1155.}

\anotecontent{FTX-ETHBULL}{List of ETHBULL holders: \url{https://bit.ly/3MSZX7P}.}

\anotecontent{FTX-DEX}{DEX transactions of FTX 3X Long Bitcoin Token (BULL) and FTX 3X Short Bitcoin Token (BEAR) on the Ethereum blockchain: \url{https://bit.ly/3pOh3uz}, \url{https://bit.ly/41Dal81}.}

\anotecontent{pionex-binance}{Among 10 LVT issuers, Pionex used the \textit{Binance Broker API} for its \textit{Futures Arbitrage Bot}, but it has been terminated since June 2021~\cite{Pionex_Binance}. After reviewing Pionex's documentation~\cite{Pionex_Guide}, it remains unclear whether \textit{Binance Futures} is still used as the leveraged product for LVTs. However, Pionex launched its own futures product in January 2023. If they no longer use \textit{Binance Futures} and rely solely on their own futures product, it appears that 148 LVTs did not have corresponding futures contracts at the time of launch (e.g., ETC3L/S, ZRX2L/S, XLM3L/S).}

\anotecontent{FINRA}{The Financial Industry Regulatory Authority (FINRA) is a government-authorized organization that oversees U.S. equity markets by regulating member brokerage firms and exchange markets.}

\anotecontent{CITADEL}{Citadel Securities is the largest designated market maker on the New York Stock Exchange (NYSE).}

\anotecontent{iceberg}{Iceberg orders, which are large orders broken into smaller lots, are a sophisticated trading algorithm used to execute rebalancing trades in smaller, more discrete chunks over time.}

\anotecontent{coop-debt}{\textsl{Index Coop} uses money market protocols on Ethereum (e.g., Compound protocol) that offer permissionless borrowing and lending capabilities~\cite{IndexCoop_FLI_01}.}

\anotecontent{notional}{The notional value represents the total value of a financial instrument or contract at its full face value (i.e., controlled money by the financial instrument). The notional value is not typically exchanged between counterparties; instead, it serves as a reference point for calculating payments or obligations~\cite{NotionalValue}.}

\anotecontent{IPO}{Taken from the initial public offering (IPO) price of a SPAC (Special Purpose Acquisition Company), which is typically set at a nominal \$10 per unit. Unlike a traditional IPO, the SPAC IPO price is not based on the valuation of an existing business but rather on future income expectations.}

\anotecontent{fund-mgmt}{Also referred to as \textsl{fund management agent}, \textsl{fund management party}, or \textsl{certified fund manager}.}

\anotecontent{performance}{Returns will be slightly lower after deducting fund management fees, accounting for market volatility, interest paid on borrowing, and other associated expenses.}

\anotecontent{imp}{LeverEdge implementation on the Testnet: \url{http://tiny.cc/ikblzz}}

\anotecontent{parimutuel}{A betting system where all bets of a particular type are aggregated into a pool, and the payout odds are determined by distributing the pool among all winning bets.}

\anotecontent{TorosETH}{arbiscan.io/address/0xf715724abba480d4d45f4cb52bef5ce5e3513ccc\#code\\arbiscan.io/address/0xad38255febd566809ae387d5be66ecd287947cb9\#code}

\anotecontent{sUSD}{sUSD is a synthetic stablecoin issued by the Synthetix protocol.}

\anotecontent{inverse}{In other words, debt-based short LVTs are restricted to an inverse exposure of 1:1, as opposed to higher leverage \(x\):1 ratios such as 3:1 or 5:1.}

\anotecontent{evm}{A decentralized computing environment that executes smart contracts on the Ethereum network.}

\anotecontent{fees}{For simplicity, we have omitted fees in example calculations. However, it is included in the table to ensure greater accuracy. As a result, there may be slight differences between the example and the values presented in the table. }

\anotecontent{test}{\textsl{Goerli} and \textsl{Sepolia} are two test networks launched in 2019 and 2021. Ethereum developers use them to test their applications before deploying on the Mainnet.}

\anotecontent{gwei}{Gwei is the standard unit for expressing gas prices, where 1 Gwei equals \( 0.000000001 \) ETH, or \( 10^{-9} \) ETH. Since gas prices are typically small fractions of Ether, using Gwei simplifies the representation, making it more practical by avoiding cumbersome decimal places in ETH. For example, a gas price of 20 Gwei is much easier to interpret than 0.000000020 ETH.}

\anotecontent{perps}{Perpetual Futures are also called Perpetual Swaps due to their structural similarity to traditional swap contracts (\ie Continuous Funding, No Expiry Date, \etc).}

\anotecontent{dated}{Also known as fixed-expiry futures contracts.}

\anotecontent{contango}{When the future prices are higher than the spot price}

\anotecontent{backwardation}{When future prices are lower than the spot price}

\anotecontent{dynamic}{Rates that fluctuate in response to market conditions.}

\anotecontent{fixed}{A fixed rate for a specific period, with the possibility of adjustment over time.}

\anotecontent{lending}{Aave App: \url{https://app.aave.com/}, Compound App: \url{https://app.compound.finance/}}

\anotecontent{impl1}{\url{https://rinkeby.etherscan.io/address/0x8825bac68a3f6939c296a40fc8078d18c2f66ac7}}
	
\anotecontent{impl2}{\url{https://rinkeby.etherscan.io/address/0x5d148c948c01e1a61e280c8 b2ac39fd49ee6d9c6}}

\anotecontent{ssga}{State Street Bank and Trust Company (SSGA) is one of the three dominant companies in the ETF market, with a 14.01\% market share, following BlackRock and Vanguard, which have 33.64\% and 29.16\%, respectively~\cite{Top_ETF_Issuer}.}

\anotecontent{SP500}{The S\&P 500 index comprises 500 of the top publicly traded companies in the U.S. It was launched in 1957 by the credit rating agency Standard and Poor's~\cite{Investo_SP500}.}

\anotecontent{underlying}{The underlying asset can be stocks, market indexes (e.g., S\&P 500, NASDAQ-100, etc.), commodities (e.g., gold, oil, corn, etc.), or any asset with a price.}

\anotecontent{vol-drag}{Also referred to as \textsl{volatility decay} or \textsl{volatility erosion}.}